---
title: "How to generate an `annotation_features.txt` file"
author: "Miguel Cosenza"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
  github_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

In this document I am including a small example on how to generate a `annotation_features.txt` file to be used as an input to do 'selected' FDR control after `limma` on a interestin features.

__Note__: the outputs that can be generated in this example would not match the ones in the sample data. This document is intender to provide a guide on how to approach such a problem of creating the `annotation_features.txt`. You need to adapt it so the IDs in your `annotation_features.txt` file would match the ones in your `input_limma.txt` file.

# Example based on annotated semi-specific peptides

We already have a script that allows us to annotate our peptides regarding their specificity ([Mapping peptides to proteins in FASTA - Annotate](https://github.com/MiguelCos/mapping_peptides_to_proteins_from_fasta_file)) and we can use that to create our `annotation_features.txt` file.

## First load the file of annotated peptides

```{r}
library(tidyverse)
library(here)

annot_peptides <- read_tsv(here("results/peptide_annotation_pif75_32searchv2.tsv"))
```

## Then select the interesting feature  

Take a look at the names of the columns

```{r}
names(annot_peptides)
```


In this case, the columns related to the unique ID of the Peptide + Protein (index) and the type of specificity.

__First we create our `index` variable so it matches the one in the `input_limma.txt` file.__

```{r}
annot_peptides_2 <- mutate(annot_peptides, # annotated peptides table as input
                           index = paste(protein_id, Peptide, "_")) # new variable index is created by concatenating protein ID and peptide.
```

__Then we select the interesting columns__

In this case: index and semi_type (containing the specificity information per peptide/feature)  

```{r}
annotation_features <- dplyr::select(annot_peptides_2,
                                     ID = index, # changed index to ID column name
                                     feature_category = semi_type)  # changed semi_type to feature_category column name
```

We can now save the `annotation_features.txt` file

```{r}
write_delim(annotation_features,
            file = here("sample/data/annotation_features_semi_try.txt"), 
            delim = "\t")
```

# Example based on protein names from headers

In the case of metaproteomics studies, we might be interested in labelling proteins as 'human' or 'non-human/bacteria'.

If we have the complete Uniprot identifier of the proteins, we can do that annotation easily.

We load a sample dataset containing protein headers/IDs in the first column

```{r}
proteins_w_headers <- read_tsv("sample/data/sample_file_ids_header.tsv")  
```

If we check the first 6 rows, we see that the first column contain the protein headers names from the fasta file. We can use that to know if it comes from bacteria or human.

```{r}
head(proteins_w_headers)
```

Now we annotate the proteins as bacterial or human

```{r}
proteins_w_annotation <- mutate(proteins_w_headers, # input object
                                feature_category = if_else(str_detect(header_id,"_HUMAN"), 
                                                           true = "human",
                                                           false = "bacteria")) # feature category is the name that this column should have in the `annotation_features.txt`
```

If we look at the last two columns, we see that, for each protein, we have a feature annotation.

```{r}
proteins_w_annotation[24:33,c(5:8)]
```

We can now select the two interesting columns (ID and feature_category) and save them in a file.

```{r}
annotation_features2 <- dplyr::select(proteins_w_annotation,
                                     ID = header_id, # changed index to ID column name
                                     feature_category)  # changed semi_type to feature_category column name
```

```{r}
write_delim(annotation_features2,
            file = here("sample/data/annotation_features_metaprot.txt"), 
            delim = "\t")
```




